%==============================Abstract Page=================================================
\chapter*{\centerline{ABSTRACT}}
\addcontentsline{toc}{chapter}{ABSTRACT}
\thispagestyle{plain} 
% Abstract (200 to 250 Words)
\vspace{-0.5cm}

Code Connect is a revolutionary social media platform made specifically to the needs of creative it professionals and developers. With a focus on collaboration, knowledge sharing, and networking, Code Connect serves as an interactive space where creative it professionals can connect with like-minded individuals, exchange ideas, and explore new opportunities within the coding community.
The platform offers a user-friendly interface and a range of features designed to enhance the programmer's experience. Users can create personalized profiles to showcase their skills, experiences, and projects, attracting potential collaborators or employers. A comprehensive search system allows users to discover discussions.
One of Code Connect's unique strengths is Messaging system. Real-time messaging facilitates productive discussions and timely feedback among peers.
Furthermore, Code Connect encourages the sharing of code snippets, problems, and open-source projects. Users can publish their code, receive feedback, and collaborate on improvements.Fesibility studies containing Technical,Operational,Economical etc were conducted. Different Software Engineering Diagrams like ER Diagram, DFD, Activity Diagram etc for System Design were created.
Latest tools like HTML,CSS,JS and PHP along with modules like AJAX and JQuery which enhances the User Expirence in our applications were userd.Unit testing for our authenication unit was tested.
Until Now implementation of Login and Register System, Discussion Management, Profile Search, Basic UI of Messaging System, Geeking System. And things like Real time system, CV and Portfolio Management etc is yet to be implemented.
\\\\
\textbf{Keywords:}  \textit{Connection, Customized Profile, Discussion and  Messaging}
%=============================================================================================
% (a) Inclusion of three to four Keywords (Lexicographical Order)
% \newpage
% \chapter*{\centerline{AKNOWLEDGEMENT}}
% We would like to extend our heartfelt gratitude to the esteemed teachers in the \thedepartment at \thecampus for their invaluable support and guidance throughout the development of our social network application.

% First and foremost, we would like to express our deepest appreciation to \thesupervisor and \theprogramcoordinator, both our project supervisor and program coordinator, for their unwavering commitment,mentorship to our project. Their expertise and profound knowledge in this field have been very helpful in shaping our technical skills and providing invaluable insights of the projects.

% Furthermore, we would like to extend our gratitude to the entire faculty of the \thedepartment. Their dedication to fostering creativity, critical thinking, and technical proficiency has been useful in our project's development. The support and guidance received from our teachers have empowered us to transform our vision into a reality.

% Your unwavering belief in our abilities and your constant encouragement have been the driving force behind our project. Your passion for education and commitment to our growth have left an indelible impact on our personal and professional development.


% Sincerely,\\
% \theauthor\\
% \thedepartment\\
% \thecampus\\
\newpage